MCC Preference Kids

### 2019-02-11 stats/kids/kids_inf.Rmd
add kids so and pref models
update cogsci submission
add data from kids ex1 inf replication

log <- read_excel("../../MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "inf")%>%
  select(subid,experimenter,keep_drop,sex,dob)

@@

pf1 %>%
  filter(correct == 0)

@@

```{r plot by numerical age, echo = F}
p5 <- d %>%
  filter(trial != "filler1",
         trial != "filler2") %>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct))

>>>>

log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "inf")%>%
  select(subid,experimenter,keep_drop,sex,dob)

@@

#write_csv(d, "data/kids_inf_data.csv")

@@

```{r plot by numerical age, echo = F}
p5 <- d %>%
  filter(trial != "filler1",
         trial != "filler2", 
         subage != "2") %>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct))

### 2019-02-11 stats/kids/kids_inf_2.Rmd
add data from kids ex1 inf replication

#write_csv(d, "data/kids_inf_2_data.csv")

@@

>>>>

#write_csv(d, "../data/kids_inf_2_data.csv")

@@

# Joining round 1 and round 2

```{r}
files <- dir("~/Work/MCC/git-mcc/kids_info_data/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,45,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

d_raw <-raw_data %>%
  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
         subid= ifelse(subid == "181031_3", "181031_3_inf",subid),
         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
         test_date= ifelse(test_date == "18-09-12", "2018-09-12",test_date),
         experiment = "mcc_kids_inf_2")

log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "inf")%>%
  select(subid,experimenter,keep_drop,sex,dob)

d2 <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

d_sum <- bind_rows(d%>%select(-test_date),d2%>%select(-test_date)%>%filter(subage!="2"))%>%
    filter(trial != "filler1",
         trial != "filler2")

```{r}
d_sum %>%
  group_by(subage)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)
```

p_sum1 <- d_sum %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

p_sum2 <- p_sum1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p_sum1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p_sum2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

```{r plot by numerical age, echo = F}
p_sum3 <- d_sum %>%
  filter(trial != "filler1",
         trial != "filler2") %>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p_sum3, aes(x = age_num, y = correct)) +
  geom_smooth(method = "lm", se = T)+
  geom_point( alpha = .5, width = 0.02)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

lm_data_sum <- d_sum%>%
  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))

# maximal converging model
lm_sum <- glmer(correct ~ age_num + (1 | subid), 
              data = lm_data_sum, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

```{r, echo = F}
summary(lm_sum)
```

### 2019-02-11 stats/kids/kids_pref_2.Rmd
add data from kids ex1 inf replication

```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = FALSE)
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)

@@

The following two plots suggest some sort of linear developmental trajectory.

@@

```{r plot by numerical age}
p5 <- d %>%
  filter(trial_type == "test") %>%
  group_by(change,age_num, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p5, aes(x = age_num, y = correct, col = change)) +
  geom_smooth(method = "loess", se = T)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

>>>>

```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = FALSE)

###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)

@@

@@

```{r plot by numerical age}
p5 <- d %>%
  filter(trial != "train") %>%
  group_by(speakerChange,age_num, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p5, aes(x = age_num, y = correct, col = speakerChange)) +
  geom_smooth(method = "lm", se = T)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```
